\section{State Estimation}
\label{state_estimation}

This section discusses the state estimation algorithms 
implemented in Odisseus. 

\subsection{Extended Kalman Filter}
\label{extended_kalman_filter}
The Extended Kalman Filter is a state estimation technique for non-linear systems. 
It is an extension of the very popular Kalman Filter (see \url{https://en.wikipedia.org/wiki/Kalman_filter}).
Just like the original Kalman Filter algorithm, the EKF has also two steps namely predict and update. 
The main difference of EKF over Kalman Filter is that it introduces a linearization of the non-linear system. 
Overall the algorithm is as follows

\subsubsection{Predict}

At this step an estimate of both the state vector $\mathbf{x}$ and the covariance matrix $\mathbf{P}$ is made.
This is done according to

\begin{equation}
\bar{\mathbf{x}}_k = \mathbf{f}(\hat{\mathbf{x}}_{k-1}, \mathbf{u}_k, \mathbf{w}_k)
\end{equation}

where $\mathbf{f}$ is described by equations \ref{equ1},  \ref{equ2} and \ref{equ3}. $\hat{\mathbf{x}}_{k-1}$ is the state at the previous
time step. $\mathbf{u}_k, \mathbf{w}$ are the input vector and error vector associated with the process. The covariance matrix is estimated via 

\begin{equation}
\bar{\mathbf{P}}_k = \mathbf{F}_k \mathbf{P}_{k-1} \mathbf{F}_{k}^T + \mathbf{L}_k\mathbf{Q}_k\mathbf{L}_{k}^T
\end{equation}

where $\mathbf{F}$ is the Jacobian matrix of $\mathbf{f}$ with respect to the state variables. 
$\mathbf{Q}_k$ is the covariance matrix of the error and $\mathbf{L}_k$ is the Jacobian matrix of the motion
model, i.e. $\mathbf{f}$, with respect to $\mathbf{w}$.

\subsubsection{Update}

The update step established the predicted state vector and covariance matrix. Overall this step is summarized by
the equations below

\begin{equation}
\mathbf{S}_k = \mathbf{H}_k \bar{\mathbf{P}}_k \mathbf{H}_{k}^T + \mathbf{M}_k\mathbf{R}_k\mathbf{M}_{k}^T
\end{equation}

\begin{equation}
\mathbf{K}_k = \bar{\mathbf{P}}_k \mathbf{H}_{k}^T\mathbf{S}_{k}^{-1}
\label{gain_matrix} 
\end{equation} 

\begin{equation}
\mathbf{x}_{k} = \bar{\mathbf{x}}_{k} + \mathbf{K}(\mathbf{z}_k - \mathbf{h}(\bar{\mathbf{x}}_k, \mathbf{v}_k))
\end{equation}

\begin{equation}
\mathbf{P}_k = (\mathbf{I} - \mathbf{K}_k\mathbf{H}_k)\bar{\mathbf{P}}_k
\end{equation}

where $\mathbf{H}$ is the Jacobian matrix of the observation model $\mathbf{h}$. $\mathbf{M}$ is the Jacobian matrix of 
the observation model with respect to the error vector $\mathbf{v}$.  $\mathbf{K}$ is the
gain matrix and $\mathbf{R}$ is the covariance matrix related to the error vector $\mathbf{v}$.
 
